### 2021-03-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

\chapter{Scalable Side-channel Vulnerability Detection}\label{chapter3}
\section{Motivation}

\section{Threat Model}
We assume that an attacker shares the same hardware platform with the target.
Here are a few examples. 1) A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can start a new VM and probe the process running on the other VM.  2) In a shielding system, a malicious operating system can extract sensitive information from the protected application. 
The attacker attempts to retrieve sensitive information through address-based
side-channel attacks. The attacker has no direct access to the target's memory or cache,
but it can probe its memory or cache at each program point. In reality, the
attacker will face many possible obstacles such as the noisy observations 
of the memory or cache. However, for this project, we assume
the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
The threat model captures most cache-based and address-based side-channel attacks. 
We only consider deterministic programs and assume an attacker 
has access to the source code or binary executable of the target program.

@@

\vspace*{2pt}
\textbf{Our Solution to Challenge C3:}
Instead of feeding the formula $f_a(k_1) \neq f_a(k_2)$ into a SMT solver, we
just randomly pick up $k_1, k_2 \in K$ and test them if they can satisfy the
formula. Our solution is based on the following intuition. For most combination
of $(k_{1}, k_{2} )$, the formula $f_a(k_1) \neq f_a(k_2)$ holds. As long as
$f_a$ is not a constant function, such $k_1, k_2$ must exist. For example,
suppose each time we only have 5\% chance to find such $k_1, k_2$, then after we
test with different input combination with 100 times, we have $1 -
(1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. Such random algorithms
work well for our problem.
\section{Evaluation}

>>>>

\chapter{Scalable Side-channel Vulnerability Detection}\label{chapter3}
\section{Problem}

\section{Threat Model}
We assume that an attacker shares the same hardware platform with the target.
Here are a few examples. 1) A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can start a new VM and probe the process running on the other VM.  2) In a shielding system, a malicious operating system can extract sensitive information from the protected application. 3) An user level application can probe some sensitive information inside the kernel. 
The attacker attempts to retrieve sensitive information through address-based
side-channel attacks. The attacker has no direct access to the target's memory or cache,
but it can probe its memory or cache at each program point. In reality, the
attacker will face many possible obstacles such as the noisy observations 
of the memory or cache. However, for this project, we assume
the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
The threat model captures most cache-based and address-based side-channel attacks. 
We only consider deterministic programs and assume an attacker 
has access to the source code or binary executable of the target program.

@@

\vspace*{2pt}
\textbf{Our Solution to Challenge C3:}
Instead of feeding the formula $f_a(k_1) \neq f_a(k_2)$ into a SMT solver, we
just randomly pick up $k_1, k_2 \in K$ and test them if they can satisfy the
formula. Our solution is based on the following intuition. For most combination
of $(k_{1}, k_{2} )$, the formula $f_a(k_1) \neq f_a(k_2)$ holds. As long as
$f_a$ is not a constant function, such $k_1, k_2$ must exist. For example,
suppose each time we only have 5\% chance to find such $k_1, k_2$, then after we
test with different input combination with 100 times, we have $1 -
(1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. Such random algorithms
work well for our problem.

\section{Design and Implementation}
\subsection{Trace Logging}
The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI). 
We run a program with the concrete input under the DBI to record execution traces.
The trace data has the following information:
\begin{itemize}
     \item Each instruction mnemonics and its memory address.
     \item The operands of each instruction and their concrete values during the runtime.
     \item The value of EFLAGS register. 
     \item The memory address and the length of the sensitive information.
      Most crypto libraries stores sensitive information in arrays,
      variables or contiguous buffer.
\end{itemize}

\subsection{Instruction Level Symbolic Execution}
\label{InstructionSE}
The primary purpose of the step is to generate constraints of the input sensitive information from the execution trace. If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies those constraints, as an attacker, he will have the same observations on control-flow transfers and data-access patterns.

The tool runs symbolic execution on top of execution traces. At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer. For other data in the register or memory at the beginning, we use actual values from the runtime information collected during the runtime. During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula. The formula is made up of concrete values and the input key as the symbols accumulated through the symbolic execution.
For each formula, the tool will check weather it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ). If so, the tool will only use the concrete values in the following symbolic execution.

\subsubsection{Verification and Optimization}
We run the symbolic execution (SE) on top of x86 instructions. In other words, we do not rely on any intermediate languages to simplify the implementation of symbolic execution. While the implementation itself has a lot of benefits (Better performance, accurate memory model), we need to implement the symbolic execution rules for each x86 instruction. 
However, due to the complexity of x86, it is inevitable to make mistakes. Therefore, we verify the correctness of the SE engine during the execution. 
The tool will collect the runtime information (Register values, memory values) and compare them with the formula generated from the symbolic execution. Whenever the tool finishes the symbolic execution of each instruction, the tool will compare the formula for each symbol and its actual value. If the two values do not match, we check the code and fix the error. Also, if the formula does not contain any symbols, the tool will use the concrete value instead of symbolic execution.

\subsubsection{Secret-dependent control-flows}
An adversary can infer sensitive information from secret dependent control-flows. There are two kinds of control-transfer instructions: the unconditional control-transfer instructions and the conditional transfer instructions.
The unconditional instructions, like CALL, JUMP, RET transfer control from one code segment location to another. Since the transfer is independent of the input sensitive information, an attacker was not able to infer any sensitive information from the control-flow. 
So the unconditional control-transfer does not leak any information based on our threat model. During the symbolic execution, we update the register information and memory cells with new formulas accordingly.

The conditional control-flow transfer instructions, like conditional jumps, depending on CPU states, may or may not transfer control flows. For conditional jumps, the CPU will test if certain condition flag 
(e.g., CF = 0, ZF =1) is met and jump to certain branches, respectively.
The symbolic engine will compute the flag and represent the flag in a symbol 
formula. Because we are running on a symbolic execution on an execution trace, 
we know which branch is executed.
If a conditional jump uses the CPU status flag, we will generate the constraint accordingly.

\section{Evaluation}
